 

### 2023-06-26 markdown/Thesis.Rmd
formating

\Large
\doublespacing
{\bf Design and implementation of analysis pipeline for single cell type proteomics data} 
presenting ProteoScanR \& Proteomics Workbench

@@

\normalsize
\singlespacing
By

@@

{\bf Lukas Gamp}
01630003

@@

in partial fulfillment of the requirement \\for the degree of MSc \\in Bioinformatics

@@

Main Supervisor: 
Dr. DI(FH) Gerhard Duernberger

External Supervison:
Assoc. Prof. Ujjwal Neogi, M.Sc. PhD

Second examiner:
FH-Prof. Dr. Alexandra Graf

>>>>

\Large
\doublespacing
{\bf Design and implementation of analysis pipeline for single cell type proteomics data} 
\\ presenting ProteoScanR \& Proteomics Workbench

@@

\normalsize
\singlespacing

@@

{\bf Lukas Gamp}
\\ 01630003

@@

In partial fulfillment of the requirement \\for the degree of MSc \\in Bioinformatics

@@

\doublespacing
\doublespacing
Main Supervisor: Dr. DI(FH) Gerhard Duernberger \\
External Supervison: Assoc. Prof. Ujjwal Neogi, M.Sc. PhD \\
Second examiner: FH-Prof. Dr. Alexandra Graf \\

### 2023-06-26 markdown/appendix.Rmd
results until stats finished
formating

## Cells sorting protocol
\begin{enumerate}
\item 96 single cells from each donor were sorted into a single plate. Each well contained a single cell. As such, 12 different plates containing single cells from 12 different donors were prepared. 
\item Carrier plates were also prepared. In the carrier plates, 100 cells from one donor were sorted into each well. 24 such wells (3 columns) were prepared for each donor.
\end{enumerate}

@@

### R-version info

\begin{verbatim}
R version 4.3.0 (2023-04-21)
Platform: x86_64-pc-linux-gnu (64-bit)
Running under: Ubuntu 22.04.2 LTS

 [1] visNetwork_2.1.2            snowfall_1.84-6.2          
 [3] snow_0.4-4                  piano_2.16.0               
 [5] org.Hs.eg.db_3.17.0         AnnotationDbi_1.62.1       
 [7] infotheo_1.2.0.1            clusterProfiler_4.8.1      
 [9] plotly_4.10.1               sva_3.48.0                 
[11] BiocParallel_1.34.2         genefilter_1.82.1          
[13] mgcv_1.8-42                 nlme_3.1-162               
[15] impute_1.74.1               CONSTANd_1.8.0             
[17] limma_3.56.1                scater_1.28.0              
[19] scuttle_1.10.1              reshape2_1.4.4             
[21] dplyr_1.1.2                 magrittr_2.0.3             
[23] ggplot2_3.4.2               SingleCellExperiment_1.22.0
[25] scp_1.10.0                  QFeatures_1.10.0           
[27] MultiAssayExperiment_1.26.0 SummarizedExperiment_1.30.1
[29] Biobase_2.60.0              GenomicRanges_1.52.0       
[31] GenomeInfoDb_1.36.0         IRanges_2.34.0             
[33] S4Vectors_0.38.1            BiocGenerics_0.46.0        
[35] MatrixGenerics_1.12.0       matrixStats_0.63.0         
[37] spsComps_0.3.2.1            DT_0.28                    
[39] shinydashboard_0.7.2        shinyWidgets_0.7.6         
[41] shiny_1.7.4                
\end{verbatim}

>>>>

## Wet lab
### Cells sorting protocol
\begin{enumerate}
\item 96 single cells from each donor were sorted into a single plate. Each well contained a single cell. As such, 12 different plates containing single cells from 12 different donors were prepared. 
\item Carrier plates were also prepared. In the carrier plates, 100 cells from one donor were sorted into each well. 24 such wells (3 columns) were prepared for each donor.
\end{enumerate}

@@

## Dry lab
### R-version info

```{r load_libraries, message=FALSE, warning=FALSE, include=FALSE}
library("shiny")
library("shinyWidgets")
library("shinydashboard")
library("DT")
library("spsComps")

library("scp")
library("SingleCellExperiment")
library("ggplot2")
library("magrittr")
library("dplyr")
library("reshape2")
library("scater")
library("limma")
library("CONSTANd")
library("stats")
library("impute")
library("sva")
library("plotly")
library("clusterProfiler")
library("infotheo")
library("org.Hs.eg.db")
library("AnnotationDbi")
library("piano")
library("snowfall")
library("parallel")
library("visNetwork")
```

```{r session_info, echo=FALSE}
sessionInfo()
```

### 2023-06-26 markdown/methods.Rmd
formating

```{r data_processing_pipeline_flowchart_vertical, echo=FALSE, fig.height=27, fig.width=17, fig.align='center', fig.cap="Flowchart presenting the processing by ProteoScanR"}
library(Gmisc, quietly = TRUE)
library(glue)
library(htmlTable)
library(grid)
library(magrittr)

>>>>

```{r data_processing_pipeline_flowchart_vertical, echo=FALSE, fig.height=27, fig.width=17, out.width="90%", fig.align='center', fig.cap="Flowchart presenting the processing by ProteoScanR"}
library(Gmisc, quietly = TRUE)
library(glue)
library(htmlTable)
library(grid)
library(magrittr)
